\LARGE \bf Mixed Non-Bayesian and DeGroot Learning

### 2012-12-11 docs/paper.tex

In order to characterize the effect of naive DeGroot nodes on Non-Bayesian social learning we simulated the time taken for convergence versus the ratio of Non-Bayesian to DeGroot nodes in a network.  This simulation was performed for a several graph types: Barabasi-Albert preferential attachment~\cite{Barabasi}, Kleinberg small-world~\cite{KleinbergSmallWorld}, Eppstein power law~\cite{Eppstein}, and the complete graph.  To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian received any signals; the other 50\% needed to rely completely on learning from their neighbors.  Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.

\begin{figure*}[t]
%\hspace*{0.1in}
%\centerline{\includegraphics[scale=0.8]{figures/nb_ratio}}
\centering
\includegraphics[width=0.9\textwidth]{figures/nb_ratio}
\caption{Time to convergence decreases as the ratio of Non-Bayesian to DeGroot nodes decreases}
\label{fig:nb_ratio}
\end{figure*}

>>>>

In order to characterize the effect of naive DeGroot nodes on Non-Bayesian social learning we simulated time taken for convergence versus the ratio of Non-Bayesian to DeGroot nodes in a network.  This simulation was performed for a several graph types: Barabasi-Albert preferential attachment~\cite{Barabasi}, Kleinberg small-world~\cite{KleinbergSmallWorld}, Eppstein power law~\cite{Eppstein}, and the complete graph.  To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian nodes received any signals; the other 50\% needed to rely completely on learning from their neighbors.  Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.

\begin{figure*}[h]
%\hspace*{0.1in}
%\centerline{\includegraphics[scale=0.8]{figures/nb_ratio}}
\centering
\includegraphics[width=0.9\textwidth]{figures/nb_ratio}
\caption{Time to convergence decreases as the ratio of Non-Bayesian to DeGroot nodes decreases}
\label{fig:nb_ratio}
\end{figure*}
